Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-03-07 ms.tex
Shuffle noise model to Setup section
...and make the list of parameters prettier

\documentclass{iopart}
\usepackage{amsopn}
\usepackage{iopams}
\usepackage{graphicx}
\usepackage{bib/aas_macros}
\usepackage[colorlinks]{hyperref}
\input{ligo-acronyms/acronyms}

@@

>>>>

\documentclass{iopart}
\usepackage{arydshln}
\usepackage{multirow}
\usepackage{amsopn}
\usepackage{iopams}
\usepackage{graphicx}
\usepackage{bib/aas_macros}
\usepackage[colorlinks]{hyperref}
\input{ligo-acronyms/acronyms}

@@

A laser interferometer senses \acp{GW} by transducing differential changes in arm length to a digitized photocurrent time series. In the angular frequency domain, a single detector's observation $X(\omega)$ is
%
\begin{equation}\label{eq:signal-model}
	X (\omega) = H (\omega; \boldsymbol\theta) + N (\omega),
\end{equation}
%
where $H (\omega; \boldsymbol\theta)$ is the \ac{GW} signal, given a parameter vector $\boldsymbol\theta$ that describes the \ac{GW} source, and $N (\omega)$ is the detector's \ac{WSS} Gaussian noise with \ac{PSD} $S(\omega)$. The likelihood, or the probability of obtaining the observation $X(\omega)$ conditioned on the value of $\boldsymbol\theta$, is Gaussian, with the log\nobreakdashes-likelihood proportional to:
%
\begin{equation}\label{eq:gaussian-likelihood}
	\mathcal{L}(X; \boldsymbol\theta) = p(X | \boldsymbol\theta)
		\propto \exp \left[
		- \frac{1}{2} \int_0^\infty \frac{\left|X (\omega)
			- H(\omega; \boldsymbol\theta) \right|^2}{S(\omega)} \, \mathrm{d}\omega
	\right].
\end{equation}

A \ac{CBC} source is described by a 15\nobreakdashes-dimensional parameter vector,
\begin{equation}
    \boldsymbol\theta = \begin{array}{l@{}l}
            \left[
            \begin{array}{c}
                \alpha \\
                \delta \\
                t_\oplus \\
                \iota \\
                \psi \\
                \phi_c \\
                \hdashline[1pt/1pt]
                m_1 \\
                m_2 \\
                \mathbf S_1 \\
                \mathbf S_2
            \end{array}
            \right] &
            \begin{array}{l}
                \left.
                \begin{array}{p{4cm}}
                    right ascension \\
                    declination \\
                    arrival time at geocenter \\
                    inclination angle \\
                    polarization angle \\
                    coalescence phase \\
                    \hdashline[1pt/1pt]
                \end{array}
                \quad \right\} \textnormal{extrinsic} \\
                \left.
                \begin{array}{p{4cm}}
                    first component's mass \\
                    second component's mass \\
                    first component's spin \\
                    second component's spin
                \end{array}
                \quad \right\} \textnormal{intrinsic}
            \end{array}
        \end{array}
\end{equation}

In this work we restrict ourselves to non-spinng sources, where $\mathbf{S}_1=\mathbf{S}_2=0$. Removing nuisance parameters requires either replacing them with their measured values or marginalizing over them. The chirp mass is typically well measured by the detection pipeline, so we use the maximum likelihood value, $\hat{\mathcal{M}}$, for it. We marginalize over the other variables using a uniform prior, i.e.
\begin{equation}
p(\alpha,\delta,D_L|d) = \int\, d\tau_\oplus p_U(\tau_\oplus) d\phi_c p_U(\phi_c) d\phi p_U(\psi)  d\cos(\iota) p_U(\cos(\iota)) p(\alpha,\delta,D_L,\tau_\oplus,\phi_c,\psi,\cos(\iota)|d),
\end{equation}
where $p_U(x)$ denotes a uniform distribution in $x$.
